---
title: "Getting started with R"
author: Your name here
date: today
format: html
---

### Exercise 1 {#sec-1}

* Create a vector of the letters A, B and C.

```{r}
# Your answer in code
N<-c("A","B","C")
```
> Your answer as text



* Assign the vector to a variable `my_letters`
```{r}
# Your answer in code
my_letters<-N

```


* Check the what happens when you run `letters` (just this) on the command line.
```{r}
# Your answer in code
letters
```

> Your answer as text

alphabet


* What happens when you concatenate two vectors? Add `c(my_letters , my_letters)`
```{r}
# Your answer in code
c(my_letters,my_letters)

```

> Your answer as text

the other vector is paste next the first vector, in this case I have twice my letters

* Add the number 1 to letters. What happens to the type of the vector?
```{r}
# Your answer in code
new<-c(my_letters,1)
typeof(new)
```

> Your answer as text

The type of the vector continue as character when y added 1 

### Exercise 2


1. Create a vector `my_vec` with the numbers from 1 through 8.
2. Apply the operation `+2` to the vector/
3. Add the vector containing 1, 2, 3, 4 to `my_vec`. What do you observe?

```{r}
# Your answer in code

#1.
my_vec<-c(1:8)
#2
my_vec<-my_vec+2
#3
b<-c(1,2,3,4)
my_vec+b
```



### Exercise 3

* Consider the R output of the matrix below:

```
 [,1] [,2]
 [1,]    4    1
 [2,]    9    5
 [3,]   10    7
```

1. What was one of the correct commands used to write this matrix?
2. Assign the matrix as `A`
3. Check the dimensions
4. Extract the element `5`
5. Add the vector `c(0,0,0)` as a new column and update `A`
6. Modify the element 4 to `0`
7. Compute the transpose of `A`

```{r}
# Your answer in code
#1.

M<-matrix(c(4,9,10,1,5,7),nrow = 3,ncol=2)

#2.

A<-M

#3 
dim(A)

#4

A[5]

#5
v<-c(0,0,0)
A<-cbind(M,c(0,0,0))

#6
A[4]<-0


#7
t(A)
```


8. Are any values in `A` larger than 10? 
```{r}
# Your answer in code

A>10
```

9. Are all values in `A` smaller than 10?
```{r}
# Your answer in code
A<10
```

### Exercise 4

1. Create a function that sums up two values even if provided as characters values

```{r}
# Your answer in code

sum<-function(x,y){
  y+x
}



```


### Exercise 5

1. Create a function that returns the mean, median and standard deviation.

```{r}
# Your answer in code

stat<-function(x){
  print(mean(x))
  print(median(x))
  print(sd(x))
  
}
stat(my_vec)
```


### Exercise 6
1. Create a pipe statement that counts the number of NAs in vector containing numbers, characters and missing values.
The output of `c('1' , "a", NA, "2", NA)` should be 2.

```{r}
# Your answer in code


c('1' , "a", NA, "2", NA) |> 
  is.na() |> 
  sum()


```


